Through the eyes of the teacher

### 2021-02-16 paper_1/paper_1_supplement_new_table.tex
added alpha for each scale (self-assessment/students)

The table provides an overview over the mean, the range and standard deviation of all scales.

@@

\caption{\label{tab:table all scales}Mean values of all scales}

@@

\begin{tabular}{lllll}
\toprule
scale & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{SD scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae}\\
\midrule
Activation and support & 2.45 & 1.37 & 0.00 & 4.00\\
Clarity and structuredness & 3.41 & 0.81 & 1.00 & 4.00\\
Classroom management & 2.97 & 0.94 & 1.00 & 4.00\\
Natural behaviour & 3.28 & 0.74 & 2.00 & 4.00\\
Positive climate and motivation & 3.27 & 0.89 & 0.00 & 4.00\\
Presence: posture/gaze & 3.10 & 0.96 & 0.00 & 4.00\\
Presence: verbal and non-verbal intervention & 3.07 & 0.82 & 1.00 & 4.00\\
Presence: voice & 3.40 & 0.72 & 2.00 & 4.00\\
\bottomrule
\end{tabular}

>>>>

Table \ref{tab:table-all-scales-self-assessment} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the teachers' self-assessment.

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.as.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.85      0.87    0.85      0.69 6.8 0.095  2.5 0.97     0.62
## 
##  lower alpha upper     95% confidence boundaries
## 0.67 0.85 1.04 
## 
##  Reliability if an item is dropped:
##                  raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r
## af_beiträge           0.75      0.76    0.62      0.62  3.2    0.169    NA
## af_nachdenken         0.71      0.74    0.59      0.59  2.9    0.185    NA
## af_wechselseitig      0.93      0.93    0.87      0.87 13.7    0.049    NA
##                  med.r
## af_beiträge       0.62
## af_nachdenken     0.59
## af_wechselseitig  0.87
## 
##  Item statistics 
##                  n raw.r std.r r.cor r.drop mean   sd
## af_beiträge      8  0.90  0.92  0.90   0.80  3.0 0.93
## af_nachdenken    8  0.92  0.93  0.92   0.81  2.4 1.06
## af_wechselseitig 8  0.86  0.82  0.65   0.62  2.0 1.31
## 
## Non missing response frequency for each item
##                     1    2    3    4 miss
## af_beiträge      0.00 0.38 0.25 0.38    0
## af_nachdenken    0.25 0.25 0.38 0.12    0
## af_wechselseitig 0.50 0.25 0.00 0.25    0
\end{verbatim}

\begin{verbatim}
## Warning in alpha(self.cs.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( ks_sichtbar ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Warning in sqrt(Vtc): NaNs wurden erzeugt
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.cs.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r   S/N  ase mean   sd median_r
##      -0.76      -1.1   -0.36     -0.36 -0.53 0.94  2.8 0.53    -0.36
## 
##  lower alpha upper     95% confidence boundaries
## -2.6 -0.76 1.08 
## 
##  Reliability if an item is dropped:
##                 raw_alpha std.alpha G6(smc) average_r   S/N alpha se var.r
## ks_sichtbar         -0.75     -0.36    0.13     -0.36 -0.26       NA     0
## ks_verständlich     -0.17     -0.36    0.13     -0.36 -0.26       NA     0
##                 med.r
## ks_sichtbar     -0.36
## ks_verständlich -0.36
## 
##  Item statistics 
##                 n raw.r std.r r.cor r.drop mean   sd
## ks_sichtbar     8  0.88  0.57   NaN  -0.36  3.1 1.13
## ks_verständlich 8  0.13  0.57   NaN  -0.36  2.5 0.53
## 
## Non missing response frequency for each item
##                    1    2    3   4 miss
## ks_sichtbar     0.12 0.12 0.25 0.5    0
## ks_verständlich 0.00 0.50 0.50 0.0    0
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.cm.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.83      0.82    0.93      0.54 4.6 0.084  2.4 0.72     0.55
## 
##  lower alpha upper     95% confidence boundaries
## 0.67 0.83 1 
## 
##  Reliability if an item is dropped:
##                raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r med.r
## km_aktiv            0.84      0.83    0.83      0.62 5.0    0.091 0.049  0.57
## km_klar             0.71      0.68    0.86      0.42 2.2    0.172 0.167  0.44
## km_mitbekommen      0.89      0.89    0.94      0.74 8.4    0.070 0.033  0.82
## km_ungestört        0.65      0.63    0.70      0.37 1.7    0.182 0.101  0.53
## 
##  Item statistics 
##                n raw.r std.r r.cor r.drop mean   sd
## km_aktiv       8  0.73  0.73  0.71   0.56  2.0 0.76
## km_klar        8  0.93  0.92  0.90   0.84  2.5 1.07
## km_mitbekommen 8  0.60  0.62  0.51   0.40  2.8 0.71
## km_ungestört   8  0.97  0.97  0.99   0.93  2.5 0.93
## 
## Non missing response frequency for each item
##                   1    2    3    4 miss
## km_aktiv       0.25 0.50 0.25 0.00    0
## km_klar        0.12 0.50 0.12 0.25    0
## km_mitbekommen 0.00 0.38 0.50 0.12    0
## km_ungestört   0.12 0.38 0.38 0.12    0
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.nb.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##        0.9       0.9    0.87      0.76 9.4 0.061  2.8 0.71     0.76
## 
##  lower alpha upper     95% confidence boundaries
## 0.78 0.9 1.02 
## 
##  Reliability if an item is dropped:
##             raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r med.r
## m_fiktiv         0.91      0.91    0.83      0.83 10.1    0.065    NA  0.83
## m_natürlich      0.81      0.81    0.68      0.68  4.2    0.135    NA  0.68
## m_verhalten      0.86      0.86    0.76      0.76  6.4    0.096    NA  0.76
## 
##  Item statistics 
##             n raw.r std.r r.cor r.drop mean   sd
## m_fiktiv    8  0.88  0.89  0.79   0.75  3.0 0.76
## m_natürlich 8  0.94  0.94  0.92   0.87  2.6 0.74
## m_verhalten 8  0.92  0.91  0.86   0.81  2.9 0.83
## 
## Non missing response frequency for each item
##                2    3    4 miss
## m_fiktiv    0.25 0.50 0.25    0
## m_natürlich 0.50 0.38 0.12    0
## m_verhalten 0.38 0.38 0.25    0
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.pcm.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
##       0.78      0.78    0.97      0.37 3.5 0.11  2.9 0.61     0.41
## 
##  lower alpha upper     95% confidence boundaries
## 0.57 0.78 1 
## 
##  Reliability if an item is dropped:
##                   raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r
## lkm_ausreden           0.81      0.81    0.88      0.47 4.4     0.10 0.083
## lkm_freundlich         0.80      0.78    0.91      0.41 3.5     0.09 0.120
## lkm_interesse          0.73      0.74    0.98      0.36 2.8     0.15 0.114
## lkm_kritik             0.69      0.66    0.84      0.28 2.0     0.16 0.122
## lkm_rückmeldungen      0.67      0.68    0.79      0.30 2.1     0.18 0.088
## lkm_überlegen          0.77      0.78    0.88      0.41 3.5     0.12 0.091
##                   med.r
## lkm_ausreden       0.48
## lkm_freundlich     0.46
## lkm_interesse      0.41
## lkm_kritik         0.24
## lkm_rückmeldungen  0.41
## lkm_überlegen      0.43
## 
##  Item statistics 
##                   n raw.r std.r r.cor r.drop mean   sd
## lkm_ausreden      8  0.32  0.46  0.46   0.20  3.2 0.46
## lkm_freundlich    8  0.51  0.59  0.59   0.31  3.1 0.83
## lkm_interesse     8  0.80  0.72  0.66   0.63  2.6 1.19
## lkm_kritik        8  0.88  0.90  0.91   0.82  3.0 0.76
## lkm_rückmeldungen 8  0.91  0.86  0.87   0.85  2.5 0.93
## lkm_überlegen     8  0.66  0.60  0.60   0.48  2.6 0.92
## 
## Non missing response frequency for each item
##                      1    2    3    4 miss
## lkm_ausreden      0.00 0.00 0.75 0.25    0
## lkm_freundlich    0.00 0.25 0.38 0.38    0
## lkm_interesse     0.25 0.12 0.38 0.25    0
## lkm_kritik        0.00 0.25 0.50 0.25    0
## lkm_rückmeldungen 0.12 0.38 0.38 0.12    0
## lkm_überlegen     0.12 0.25 0.50 0.12    0
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.ppg.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.85      0.86    0.94      0.47 6.3 0.077  2.7 0.69     0.45
## 
##  lower alpha upper     95% confidence boundaries
## 0.7 0.85 1.01 
## 
##  Reliability if an item is dropped:
##                   raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r
## phb_alleangesehen      0.87      0.88    0.97      0.55 7.3    0.072 0.099
## phb_augen              0.81      0.82    0.98      0.44 4.7    0.104 0.113
## phb_blick              0.79      0.80    0.99      0.40 3.9    0.114 0.102
## phb_gestik             0.88      0.88    0.96      0.56 7.5    0.066 0.081
## phb_raum               0.88      0.89    0.97      0.57 8.1    0.068 0.078
## phb_stand              0.78      0.80    0.86      0.40 4.0    0.118 0.107
## phb_vorsichgeht        0.80      0.80    0.94      0.40 3.9    0.108 0.110
##                   med.r
## phb_alleangesehen  0.49
## phb_augen          0.45
## phb_blick          0.42
## phb_gestik         0.52
## phb_raum           0.62
## phb_stand          0.42
## phb_vorsichgeht    0.42
## 
##  Item statistics 
##                   n raw.r std.r r.cor r.drop mean   sd
## phb_alleangesehen 8  0.51  0.52  0.46   0.35  3.0 0.93
## phb_augen         8  0.85  0.84  0.83   0.76  3.4 1.06
## phb_blick         8  0.96  0.96  0.98   0.94  2.8 0.89
## phb_gestik        8  0.52  0.50  0.48   0.33  2.6 1.06
## phb_raum          8  0.43  0.45  0.36   0.26  1.8 0.89
## phb_stand         8  0.95  0.95  0.97   0.93  2.9 0.99
## phb_vorsichgeht   8  0.96  0.96  0.96   0.94  2.5 0.76
## 
## Non missing response frequency for each item
##                      1    2    3    4 miss
## phb_alleangesehen 0.12 0.00 0.62 0.25    0
## phb_augen         0.12 0.00 0.25 0.62    0
## phb_blick         0.12 0.12 0.62 0.12    0
## phb_gestik        0.12 0.38 0.25 0.25    0
## phb_raum          0.50 0.25 0.25 0.00    0
## phb_stand         0.12 0.12 0.50 0.25    0
## phb_vorsichgeht   0.12 0.25 0.62 0.00    0
\end{verbatim}

\begin{verbatim}
## Warning in alpha(self.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Warning in sqrt(Vtc): NaNs wurden erzeugt
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.pvni.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r   S/N ase mean   sd median_r
##      -0.75     -0.81   -0.42     -0.18 -0.45   1  2.8 0.35    -0.17
## 
##  lower alpha upper     95% confidence boundaries
## -2.76 -0.75 1.26 
## 
##  Reliability if an item is dropped:
##              raw_alpha std.alpha G6(smc) average_r   S/N alpha se var.r  med.r
## pi_direkt        -0.58     -0.72  -0.264    -0.264 -0.42     0.95    NA -0.264
## pi_nonverbal     -0.21     -0.22  -0.098    -0.098 -0.18     0.81    NA -0.098
## pi_zubewegen     -0.38     -0.40  -0.165    -0.165 -0.28     0.94    NA -0.165
## 
##  Item statistics 
##              n raw.r std.r r.cor r.drop mean   sd
## pi_direkt    8  0.49  0.53   NaN  -0.22  3.2 0.71
## pi_nonverbal 8  0.64  0.41   NaN  -0.30  2.4 0.92
## pi_zubewegen 8  0.20  0.46   NaN  -0.29  2.6 0.52
## 
## Non missing response frequency for each item
##                 1    2    3    4 miss
## pi_direkt    0.00 0.12 0.50 0.38    0
## pi_nonverbal 0.12 0.50 0.25 0.12    0
## pi_zubewegen 0.00 0.38 0.62 0.00    0
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.pv.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
##       0.77      0.76    0.82      0.51 3.2 0.12  2.8 0.62     0.54
## 
##  lower alpha upper     95% confidence boundaries
## 0.53 0.77 1.01 
## 
##  Reliability if an item is dropped:
##             raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r med.r
## ps_deutlich      0.65      0.70    0.54      0.54 2.32    0.213    NA  0.54
## ps_impulse       0.89      0.89    0.79      0.79 7.75    0.081    NA  0.79
## ps_klar          0.31      0.34    0.21      0.21 0.52    0.434    NA  0.21
## 
##  Item statistics 
##             n raw.r std.r r.cor r.drop mean   sd
## ps_deutlich 8  0.87  0.81  0.76   0.64  2.9 0.83
## ps_impulse  8  0.62  0.71  0.52   0.39  2.6 0.52
## ps_klar     8  0.96  0.95  0.95   0.88  2.9 0.83
## 
## Non missing response frequency for each item
##                2    3    4 miss
## ps_deutlich 0.38 0.38 0.25    0
## ps_impulse  0.38 0.62 0.00    0
## ps_klar     0.38 0.38 0.25    0
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## Warning in alpha(self.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done

## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = self.p.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N ase mean   sd median_r
##       0.74      0.74    0.73      0.18 2.8 0.1  2.7 0.42     0.18
## 
##  lower alpha upper     95% confidence boundaries
## 0.54 0.74 0.95 
## 
##  Reliability if an item is dropped:
##                   raw_alpha std.alpha G6(smc) average_r S/N var.r med.r
## phb_alleangesehen      0.71      0.70    0.74      0.16 2.3  0.20 0.159
## phb_augen              0.70      0.70    0.72      0.16 2.4  0.18 0.159
## phb_blick              0.66      0.66    0.67      0.14 1.9  0.17 0.145
## phb_gestik             0.74      0.73    0.75      0.19 2.8  0.20 0.178
## phb_raum               0.74      0.72    0.72      0.18 2.6  0.20 0.178
## phb_stand              0.65      0.65    0.67      0.14 1.9  0.17 0.129
## phb_vorsichgeht        0.68      0.66    0.68      0.14 1.9  0.18 0.096
## pi_direkt              0.76      0.76    0.75      0.21 3.1  0.21 0.273
## pi_nonverbal           0.84      0.83    0.81      0.29 4.9  0.12 0.291
## pi_zubewegen           0.76      0.76    0.78      0.21 3.1  0.21 0.214
## ps_deutlich            0.71      0.70    0.77      0.17 2.4  0.20 0.145
## ps_impulse             0.74      0.72    0.74      0.18 2.6  0.21 0.202
## ps_klar                0.68      0.66    0.69      0.14 2.0  0.19 0.130
## 
##  Item statistics 
##                   n  raw.r std.r  r.cor r.drop mean   sd
## phb_alleangesehen 8  0.617  0.65  0.644  0.495  3.0 0.93
## phb_augen         8  0.673  0.62  0.587  0.545  3.4 1.06
## phb_blick         8  0.908  0.88  0.845  0.872  2.8 0.89
## phb_gestik        8  0.453  0.38  0.257  0.280  2.6 1.06
## phb_raum          8  0.439  0.49  0.389  0.296  1.8 0.89
## phb_stand         8  0.956  0.92  0.891  0.935  2.9 0.99
## phb_vorsichgeht   8  0.893  0.87  0.834  0.859  2.5 0.76
## pi_direkt         8  0.147  0.18  0.023  0.019  3.2 0.71
## pi_nonverbal      8 -0.723 -0.71 -1.014 -0.789  2.4 0.92
## pi_zubewegen      8  0.075  0.17  0.072 -0.019  2.6 0.52
## ps_deutlich       8  0.638  0.60  0.622  0.534  2.9 0.83
## ps_impulse        8  0.376  0.47  0.452  0.291  2.6 0.52
## ps_klar           8  0.855  0.86  0.819  0.805  2.9 0.83
## 
## Non missing response frequency for each item
##                      1    2    3    4 miss
## phb_alleangesehen 0.12 0.00 0.62 0.25    0
## phb_augen         0.12 0.00 0.25 0.62    0
## phb_blick         0.12 0.12 0.62 0.12    0
## phb_gestik        0.12 0.38 0.25 0.25    0
## phb_raum          0.50 0.25 0.25 0.00    0
## phb_stand         0.12 0.12 0.50 0.25    0
## phb_vorsichgeht   0.12 0.25 0.62 0.00    0
## pi_direkt         0.00 0.12 0.50 0.38    0
## pi_nonverbal      0.12 0.50 0.25 0.12    0
## pi_zubewegen      0.00 0.38 0.62 0.00    0
## ps_deutlich       0.00 0.38 0.38 0.25    0
## ps_impulse        0.00 0.38 0.62 0.00    0
## ps_klar           0.00 0.38 0.38 0.25    0
\end{verbatim}

@@

\caption{\label{tab:table-all-scales-self-assessment}Scale analysis for teachers' self-assessment}

@@

\begin{tabular}{lllllll}
\toprule
scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis}\\
\midrule
Activation and support & 2.46 & 1.14 & 1.00 & 4.00 & 0.10 & 1.65\\
Clarity and structuredness & 2.81 & 0.91 & 1.00 & 4.00 & -0.17 & 2.17\\
Classroom management & 2.44 & 0.88 & 1.00 & 4.00 & 0.19 & 2.38\\
Natural behaviour & 2.83 & 0.76 & 2.00 & 4.00 & 0.28 & 1.84\\
Positive climate and motivation & 2.85 & 0.87 & 1.00 & 4.00 & -0.49 & 2.65\\
Presence: posture/gaze & 2.70 & 1.01 & 1.00 & 4.00 & -0.44 & 2.15\\
Presence: verbal and non-verbal intervention & 2.75 & 0.79 & 1.00 & 4.00 & -0.07 & 2.48\\
Presence: voice & 2.79 & 0.72 & 2.00 & 4.00 & 0.32 & 2.03\\
\bottomrule
\end{tabular}

Table \ref{tab:table-all-scales-students} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the students' perception of the teacher's behaviour in class.

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = stud.as.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r  S/N  ase mean   sd median_r
##       0.48       0.5    0.41      0.25 0.99 0.17  2.6 0.71     0.22
## 
##  lower alpha upper     95% confidence boundaries
## 0.14 0.48 0.82 
## 
##  Reliability if an item is dropped:
##                  raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r
## af_beiträge           0.34      0.35    0.22      0.22 0.55     0.26    NA
## af_nachdenken         0.49      0.54    0.37      0.37 1.18     0.18    NA
## af_wechselseitig      0.26      0.27    0.16      0.16 0.37     0.29    NA
##                  med.r
## af_beiträge       0.22
## af_nachdenken     0.37
## af_wechselseitig  0.16
## 
##  Item statistics 
##                   n raw.r std.r r.cor r.drop mean   sd
## af_beiträge      24  0.64  0.72  0.49   0.35  3.3 0.75
## af_nachdenken    24  0.64  0.65  0.31   0.23  2.6 0.97
## af_wechselseitig 24  0.82  0.75  0.55   0.37  2.0 1.25
## 
## Non missing response frequency for each item
##                     1    2    3    4 miss
## af_beiträge      0.04 0.04 0.50 0.42    0
## af_nachdenken    0.12 0.33 0.33 0.21    0
## af_wechselseitig 0.58 0.00 0.25 0.17    0
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = stud.cs.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
##       0.62      0.64    0.47      0.47 1.8 0.15  3.6 0.58     0.47
## 
##  lower alpha upper     95% confidence boundaries
## 0.34 0.62 0.91 
## 
##  Reliability if an item is dropped:
##                 raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r med.r
## ks_sichtbar          0.64      0.47    0.22      0.47 0.9       NA     0  0.47
## ks_verständlich      0.35      0.47    0.22      0.47 0.9       NA     0  0.47
## 
##  Item statistics 
##                  n raw.r std.r r.cor r.drop mean   sd
## ks_sichtbar     24  0.90  0.86  0.59   0.47  3.5 0.78
## ks_verständlich 24  0.81  0.86  0.59   0.47  3.6 0.58
## 
## Non missing response frequency for each item
##                    1    2    3    4 miss
## ks_sichtbar     0.04 0.04 0.25 0.67    0
## ks_verständlich 0.00 0.04 0.29 0.67    0
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = stud.cm.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.75      0.75    0.73      0.42 2.9 0.085  3.2 0.69     0.37
## 
##  lower alpha upper     95% confidence boundaries
## 0.58 0.75 0.91 
## 
##  Reliability if an item is dropped:
##                raw_alpha std.alpha G6(smc) average_r S/N alpha se  var.r med.r
## km_aktiv            0.59      0.59    0.50      0.33 1.5    0.143 0.0038  0.35
## km_klar             0.68      0.68    0.59      0.41 2.1    0.114 0.0063  0.37
## km_mitbekommen      0.76      0.76    0.73      0.52 3.2    0.085 0.0319  0.50
## km_ungestört        0.70      0.70    0.67      0.44 2.4    0.109 0.0555  0.36
## 
##  Item statistics 
##                 n raw.r std.r r.cor r.drop mean   sd
## km_aktiv       24  0.85  0.85  0.83   0.70  3.0 0.93
## km_klar        24  0.76  0.77  0.70   0.56  3.3 0.86
## km_mitbekommen 24  0.66  0.66  0.45   0.40  3.3 0.92
## km_ungestört   24  0.74  0.74  0.59   0.52  3.1 0.93
## 
## Non missing response frequency for each item
##                   1    2    3    4 miss
## km_aktiv       0.04 0.29 0.29 0.38    0
## km_klar        0.04 0.12 0.33 0.50    0
## km_mitbekommen 0.08 0.04 0.33 0.54    0
## km_ungestört   0.08 0.12 0.42 0.38    0
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = stud.nb.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
##       0.85      0.85    0.82      0.66 5.8 0.056  3.4 0.59     0.61
## 
##  lower alpha upper     95% confidence boundaries
## 0.74 0.85 0.96 
## 
##  Reliability if an item is dropped:
##             raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r med.r
## m_fiktiv         0.71      0.71    0.56      0.56 2.5    0.120    NA  0.56
## m_natürlich      0.89      0.90    0.82      0.82 8.9    0.044    NA  0.82
## m_verhalten      0.75      0.75    0.61      0.61 3.1    0.103    NA  0.61
## 
##  Item statistics 
##              n raw.r std.r r.cor r.drop mean   sd
## m_fiktiv    23  0.92  0.92  0.89   0.79  3.4 0.72
## m_natürlich 23  0.83  0.82  0.64   0.61  3.3 0.71
## m_verhalten 23  0.89  0.90  0.86   0.77  3.5 0.59
## 
## Non missing response frequency for each item
##                2    3    4 miss
## m_fiktiv    0.13 0.35 0.52    0
## m_natürlich 0.13 0.39 0.48    0
## m_verhalten 0.04 0.43 0.52    0
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = stud.pcm.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean  sd median_r
##       0.82      0.81    0.86      0.41 4.2 0.05  3.4 0.6     0.44
## 
##  lower alpha upper     95% confidence boundaries
## 0.72 0.82 0.92 
## 
##  Reliability if an item is dropped:
##                   raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r
## lkm_ausreden           0.78      0.77    0.78      0.40 3.3    0.063 0.043
## lkm_freundlich         0.85      0.86    0.86      0.54 5.9    0.048 0.014
## lkm_interesse          0.79      0.76    0.85      0.39 3.2    0.060 0.079
## lkm_kritik             0.81      0.80    0.85      0.44 3.9    0.052 0.062
## lkm_rückmeldungen      0.76      0.74    0.81      0.36 2.8    0.067 0.075
## lkm_überlegen          0.75      0.72    0.76      0.34 2.6    0.070 0.057
##                   med.r
## lkm_ausreden       0.41
## lkm_freundlich     0.54
## lkm_interesse      0.42
## lkm_kritik         0.51
## lkm_rückmeldungen  0.41
## lkm_überlegen      0.43
## 
##  Item statistics 
##                    n raw.r std.r r.cor r.drop mean   sd
## lkm_ausreden      24  0.77  0.75  0.75   0.66  3.6 0.77
## lkm_freundlich    24  0.32  0.41  0.31   0.20  3.7 0.46
## lkm_interesse     24  0.78  0.76  0.68   0.64  3.2 0.96
## lkm_kritik        24  0.68  0.65  0.54   0.51  3.2 0.88
## lkm_rückmeldungen 24  0.84  0.84  0.80   0.73  3.3 0.92
## lkm_überlegen     24  0.87  0.88  0.90   0.79  3.4 0.83
## 
## Non missing response frequency for each item
##                      1    2    3    4 miss
## lkm_ausreden      0.04 0.04 0.17 0.75    0
## lkm_freundlich    0.00 0.00 0.29 0.71    0
## lkm_interesse     0.04 0.25 0.21 0.50    0
## lkm_kritik        0.08 0.04 0.46 0.42    0
## lkm_rückmeldungen 0.08 0.04 0.33 0.54    0
## lkm_überlegen     0.04 0.08 0.29 0.58    0
\end{verbatim}

\begin{verbatim}
## Warning in alpha(stud.ppg.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( phb_stand ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## 
## Reliability analysis   
## Call: alpha(x = stud.ppg.wide[, -1])
## 
##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
##       0.59      0.54    0.74      0.14 1.2 0.11  3.2 0.39     0.17
## 
##  lower alpha upper     95% confidence boundaries
## 0.37 0.59 0.81 
## 
##  Reliability if an item is dropped:
##                   raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r
## phb_alleangesehen      0.58      0.54    0.74     0.163 1.17    0.119 0.120
## phb_augen              0.59      0.52    0.74     0.156 1.10    0.113 0.138
## phb_blick              0.34      0.26    0.47     0.055 0.35    0.187 0.074
## phb_gestik             0.43      0.36    0.66     0.085 0.56    0.160 0.106
## phb_raum               0.67      0.61    0.76     0.203 1.53    0.086 0.109
## phb_stand              0.68      0.68    0.76     0.259 2.09    0.096 0.073
## phb_vorsichgeht        0.39      0.31    0.54     0.070 0.45    0.171 0.100
##                   med.r
## phb_alleangesehen 0.182
## phb_augen         0.135
## phb_blick         0.062
## phb_gestik        0.135
## phb_raum          0.215
## phb_stand         0.215
## phb_vorsichgeht   0.062
## 
##  Item statistics 
##                    n raw.r std.r  r.cor r.drop mean   sd
## phb_alleangesehen 24  0.45 0.425  0.287  0.231  3.5 0.66
## phb_augen         24  0.33 0.455  0.291  0.158  3.6 0.49
## phb_blick         24  0.90 0.876  0.972  0.827  3.5 0.72
## phb_gestik        24  0.77 0.748  0.706  0.577  3.0 0.86
## phb_raum          24  0.40 0.256  0.085  0.048  2.1 0.97
## phb_stand         24 -0.14 0.025 -0.130 -0.295  3.7 0.46
## phb_vorsichgeht   24  0.82 0.813  0.880  0.671  3.3 0.82
## 
## Non missing response frequency for each item
##                      1    2    3    4 miss
## phb_alleangesehen 0.00 0.08 0.29 0.62    0
## phb_augen         0.00 0.00 0.38 0.62    0
## phb_blick         0.04 0.00 0.42 0.54    0
## phb_gestik        0.04 0.25 0.42 0.29    0
## phb_raum          0.33 0.33 0.25 0.08    0
## phb_stand         0.00 0.00 0.29 0.71    0
## phb_vorsichgeht   0.04 0.08 0.38 0.50    0
\end{verbatim}

\begin{verbatim}
## Warning in alpha(stud.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
## should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}

\begin{verbatim}
## Some items ( pi_direkt ) were negatively correlated with the total scale and 
## probably should be reversed.  
## To do this, run the function again with the 'check.keys=TRUE' option
\end{verbatim}
